% This is a Latex 2e document.
% This is Test 1 for sm221
% Written by David Phillips
% hi
\documentclass[10pt]{article}

\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry,xspace}
\usepackage{graphics,graphicx,psfrag}
\usepackage{enumerate,color}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{Quiz 1 - 31 August 2016}
\lhead{SA405, Fall 2017}
\rfoot{Page \thepage}

\input{preface}

%\addtolength{\oddsidemargin}{-2.0cm}
%\addtolength{\evensidemargin}{-2.0cm}
%\addtolength{\textwidth}{3.0cm}
%\addtolength{\topmargin}{-2.5cm}
%\addtolength{\textheight}{4.5cm}


\begin{document}
\begin{center}
  {\sc Solutions to Quiz 1}\\
  {\sc Instructor: Foraker}
\end{center}

\medskip

Consider the following linear program:
\[
\begin{array}{ll}
  \max & 4 x_1 + 2x_2 - 7 x_3 \\
  \mbox{s.t.} & 2 x_1 -  x_2 + 4 x_3 \leq 18 \\
  &  4 x_1 + 2 x_2 + 5 x_3 \geq 10 \\
  & x_1 , x_2 \geq 0, x_3 \leq 0.
\end{array}
\]
\begin{enumerate}
\item ({\bf 10 points}) Convert the linear program into the canonical form, i.e., all equality constraints and nonnegative variables.
\[
\begin{array}{ll}
  \max & 4 x_1 + 2x_2 + 7 x_3 \\
  \mbox{s.t.} & 2 x_1 -  x_2 - 4 x_3 + s_1 = 18 \\
  &  4 x_1 + 2 x_2 - 5 x_3 - s_2 = 10 \\
  & x_1 \geq 0, x_2 \geq 0, x_3 \geq 0, s_1 \geq 0, s_2 \geq 0.
\end{array}
\]
\red{If you got this problem wrong, you should review Sections 2.8 and 7.3. {\bf You are expected to be able to convert linear programs to canonical form.}
Review problems include 7.14 (a) - (e). To earn half of the credit back that you lost on this problem, you must hand in correct solutions to problems 7.14 (d) and (e) by Thursday, 9/7.}  
  \vfill
\item ({\bf 6 points}) Consider the system of equations $Ax=b$, where 
\[ A = \left[
\begin{array}{rrrrrrrrrr}
2 & 3 & 1 & 0 & 0\\
-1 & 1 & 0 & 2 & 1\\
0 & 6 & 1 & 0 & 3
\end{array}
\right]
\rm{and~}
b = \left[
\begin{array}{r}
1\\
1\\
4
\end{array}
\right]
\]

Determine if (1,0,-1,1,0) is a basic solution to the system.  You must justify your answer for full credit.
\newline
\red{(1,0,-1,1,0) is NOT a basic solution to the system because 
\[ \left[
\begin{array}{rrrrrrrrrr}
2 & 3 & 1 & 0 & 0\\
-1 & 1 & 0 & 2 & 1\\
0 & 6 & 1 & 0 & 3
\end{array}
\right]
\left[
\begin{array}{r}
1\\
0\\
-1\\
1\\
0
\end{array}
\right]
= \left[
\begin{array}{r}
1\\
1\\
-1
\end{array}
\right]
\neq
b 
\]
}
\red{If you got this problem wrong, you should review pp 240-241. To earn half of the credit back that you lost on this problem, you must hand in correct solutions to problem 7.16 (b) and (c) by Thursday, 9/7.}  
  \vfill

\newpage

\item ({\bf 2 points}) You are running the simplex method on a linear program whose objective function requires maximization.  You correctly calculate the reduced costs for the nonbasic variables and find that they are given by the following:  $\bar c_x = -6, \bar c_y = 7,$ and $\bar c_z = -1$.  Based on these results you should (circle one):  
\begin{enumerate}
{\bf \item continue with the simplex method}
\item stop the simplex method
\end{enumerate}
because (circle one):
\begin{enumerate} 
\item your current solution is a global optimal solution to the linear program
\item the linear program is unbounded
{\bf \item your current solution is not a global optimal solution to the linear program}
\end{enumerate}
  \vfill

\item ({\bf 2 points}) You are running the simplex method on a linear program whose objective function requires maximization.  You correctly compute an improving simplex direction, $d = [-1/4, 1, 0, -11/4, -5/4]^T$.  If the current iterate is given by $x = [6, 0, 0, 18, 5]^T$, then the maximum step size as determined by the ratio test is (circle one):  
\begin{enumerate}
\item 0
\item 24
\item 72/11
{\bf \item 4}
\item There is no maximum step size because this linear program is unbounded.
\end{enumerate}

\vfill

\red{ If you missed problems 3 or 4, review pp 277 -- 281. There are no makeup points for these problems.}
\end{enumerate}

\end{document}



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
