%  Guinness Homework Assignment -- SA405 %
\documentclass[10pt]{article}

\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry,xspace}
\usepackage{graphics,graphicx,psfrag}
\usepackage{enumerate,color}

\input{preface}

\addtolength{\oddsidemargin}{-2.0cm}
\addtolength{\evensidemargin}{-2.0cm}
\addtolength{\textwidth}{3.0cm}
\addtolength{\topmargin}{-2.5cm}
\addtolength{\textheight}{4.5cm}


\begin{document}
\begin{center}
  {\sc Guinness Assignment}\\
  {\sc SA405, Fall 2018} \\
  {\sc Instructor: Foraker}
\end{center}

\medskip

{\bf Due via Blackboard 9/7 at 2200.}

\medskip

{\it In what follows, replace {\tt YOURLASTNAME} with your last name.
  For example, the first file MIDN Smith would save would be:}

\begin{verbatim}
Smith_guinness_mcf.mod
\end{verbatim}

\medskip

{\bf To be completed for class on Thursday 8/31/17.  DO NOT SUBMIT VIA BLACKBOARD.  Wait until the due date for the overall assignment, and submit all files at that time.}
\begin{enumerate} 
\item Obtain the data {\tt Guinness.xlsx} from Blackboard. For the given data, use GUSEK to
  formulate and solve the minimum cost flow problem, i.e., {\bf do not model the
    fixed costs for opening warehouses}.
  Solve the problem to optimality and save the file as {\tt
    YOURLASTNAME\_guinness\_mcf.mod}.
\end{enumerate}

{\bf Submit your THREE model files and your text-based answer to number 3 below via Blackboard by the due date.}
\begin{enumerate}
\item  Save your previous model file as {\tt YOURLASTNAME\_guinness\_fl\_weak.mod}. Add in
  the fixed charge constraints and objective sum to the model.
  Be sure to define your warehouse $OPEN_j$ variables as
  binary. You will also need to define a new set $W$ for warehouses, and a new parameter $capacity_j$, which specifies the maximum capacity of warehouse $j$.  Also, when adding in the fixed charge constraints, use the
  formulation:
  \[
  \Sum_{\{i | (i,j) \in A\}} X_{ij} \leq capacity_j OPEN_j, \mbox{ for all $j \in \cW$}.
  \]
Solve the model. 

\item Save your previous worksheet as {\tt
    YOURLASTNAME\_guinness\_fl\_strong.mod}. Remove the weak version of the fixed charge constraints you added in Step 1 above.  Be sure to define a new set $\cB$ for breweries.  Add a strong version of the fixed charge
  constraints as follows
  \[
  X_{ij} \leq capacity_j OPEN_j, \mbox{ for all $i \in \cB$ and $j \in \cW$}.
  \]
  Solve the model.

\item Compare the solution times for the two models, and describe in complete sentences why you think one model is faster than the other.

%\item Using your strong formulation sheet, write a macro that will determine how expensive Kilgore needs to  be for the solution to change to \red{stop using Kilgore}. The macro  should double the fixed cost of opening Kilgore until the solution  changes. Run the macro to test it.

\end{enumerate}
  


\end{document}



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
