\documentclass[letterpaper,oneside,12pt]{article}%twocolumn;titlepage(separate title page)
\usepackage{pslatex}                %Times New Roman Font; Improves on-screen readability; preferred to using times package
\usepackage[margin=0.5in]{geometry}   %1in 'uniform' margin (with oneside)
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{url}
\usepackage{bm}
\usepackage{optprog}
\usepackage{lscape}
\setcounter{MaxMatrixCols}{20}
%\setlength{\headsep}{0in}           %Distance from bottom of header to the body of text on a page.
\newcommand{\rem}[1]{}
\renewcommand{\arraystretch}{1}

% **********************************************************************
% Compact itemize, enumerate and description environments %pkg enumitem
% **********************************************************************
\usepackage{enumitem}            % [FAILS w/BEAMER] Lets define enumerate spacing: \begin{enumerate}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]
\newenvironment{compitem}{\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{itemize}}
\newenvironment{compenum}{\begin{enumerate}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{enumerate}}
\newenvironment{compdesc}{\begin{description}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{description}}

\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator*{\proj}{proj}

\newcommand{\blu}{\color{blue}}
\newcommand{\bla}{\color{black}}
\begin{document}
\noindent\fbox{%
	\parbox{\textwidth}{%
		\begin{center}
		\textbf{\large{Department of Mathematics}} \\
		\textbf{\large{SA 405 - Advanced Mathematical Programming}} \\
		\textbf{\large{Quiz 2}}
		\end{center}
	}%
}

\vspace{3mm} \hspace{\fill} \textbf{Name: \underline{\hspace{6cm}}}

Luxurious Pillows INC has two fulfillment centers in Seattle and Los Angeles. They ship pillows to the DMV area through either a warehouse in Chicago or Dallas for the costs given in the table below.

\begin{center}
\begin{tabular}{r|ccccc}
& \multicolumn{5}{c}{Transportation Costs} \\
             & Chicago & Dallas & Washington DC & Baltimore & Annapolis \\
\hline
Seattle      & 15      & 25     &       -       &    -      & -  \\
Los Angeles  & 20      & 18     & -             & -         & -  \\
Chicago      & -       & -      & 17            & 15        & 20 \\ 
Dallas       & -       & -      & 22            & 13        & 12 \\
\hline
\end{tabular}
\end{center}

The fulfillment centers in Seattle and Los Angeles have supplies of 500 and 600 pillows, respectively. Likewise, DC, Baltimore, and Annapolis have demands of 300, 600, and 400; respectively. They want to meet demand at as low of a cost as possible.

\begin{enumerate}
\item (25 points) Draw the network diagram for this problem. Be sure to indicate the supply/demand of each node. \newpage

\item For the next questions, consider the following sets and variables:

\textbf{\underline{Sets}} 

Let $N$ be the set of nodes \\
Let $E$ be the set of edges

\textbf{\underline{Variables}} 

Let $x_{i,j}$ be the flow along edge $(i,j)$ for all $(i,j) \in E$.

	\begin{enumerate}
	\item (20 points) With these sets and decision variables, write the concrete objective function for 
this model. Be sure to clearly define any new sets, variables, or parameters used. 

{\blu

\[
\text{min cost: } 15 x_{s,c} + 25 x_{s,d} + \cdots + 12 x_{d,a}
\]

}
	
	\item (15 points) With these decision variables, write the (concrete) flow balance constraint for Dallas. 
{
\blu
\[
x_{S,D} + x_{LA,D} = x_{D,DC} + x_{D,B} + x_{D,A}
\]
}
	
	\item (20 points) With these sets and decision variables, write the (parameterized) balance of flow 
constraints for this model. Be sure to clearly define any new sets, variables, or parameters used.  
{\blu

Let $b_n$ be the demand$-$ supply of node $n$ for each $n \in N$

\[
\sum_{(i,n) \in E} x_{i,n} - \sum_{(n,j) \in E} x_{n,j} = b_n
\]

}
	
	\end{enumerate}
\item (20 points) Suppose that $I = \{1,2,3\}$ and $C = \{A,B\}$. Expand the following set of constraints so that they are written with no index sets (i.e., convert these constraints from parameterized to concrete form).

\[
\sum_{i \in I} r_c x_{i,c} \geq u_c \text{ for all $c \in C$}
\]

{\blu

\[
r_A x_{1,A} + r_A x_{2,A} + r_A x_{3,A} \geq u_A
\]
\[
r_B x_{1,B} + r_B x_{2,B} + r_B x_{3,B} \geq u_B
\]

}

\end{enumerate}

\end{document}
