\documentclass[letterpaper,oneside,12pt]{article}%twocolumn;titlepage(separate title page)
\usepackage{pslatex}                %Times New Roman Font; Improves on-screen readability; preferred to using times package
\usepackage[margin=0.5in]{geometry}   %1in 'uniform' margin (with oneside)
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{url}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{optprog}
\usepackage{lscape}
\setcounter{MaxMatrixCols}{20}
%\setlength{\headsep}{0in}           %Distance from bottom of header to the body of text on a page.
\newcommand{\rem}[1]{}
\renewcommand{\arraystretch}{1}

% **********************************************************************
% Compact itemize, enumerate and description environments %pkg enumitem
% **********************************************************************
\usepackage{enumitem}            % [FAILS w/BEAMER] Lets define enumerate spacing: \begin{enumerate}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]
\newenvironment{compitem}{\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{itemize}}
\newenvironment{compenum}{\begin{enumerate}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{enumerate}}
\newenvironment{compdesc}{\begin{description}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt]}{\end{description}}

\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator*{\proj}{proj}

\newcommand{\blu}{\color{blue}}
\newcommand{\bla}{\color{black}}
\begin{document}
\noindent\fbox{%
	\parbox{\textwidth}{%
		\begin{center}
		\textbf{\large{Department of Mathematics}} \\
		\textbf{\large{SA 405 - Advanced Mathematical Programming}} \\
		\textbf{\large{Quiz 4}}
		\end{center}
	}%
}

\vspace{3mm} \hspace{\fill} \textbf{Name: \underline{\hspace{6cm}}}

You're going to Six Flags this weekend and are a roller coaster enthusiast. Six Flags has 7 total roller coasters. You label them 1 to 7 and plot out the distance you'd have to walk in order to get to each roller-coaster. The following matrix gives these distances (note it's symmetric):
\[
\begin{bmatrix}
-& 10 & 12 & 7  & 13 & 8  & 9 \\
 & -  & 10 & 13 & 25 & 6  & 7 \\
 &    & -  & 21 & 23 & 12 & 10 \\
 &    &    & -  & 12 & 3  & 9   \\
 &    &    &    & -  & 20 & 8   \\
 &    &    &    &    & -  & 3   \\
 &    &    &    &    &    & -
\end{bmatrix}
\]

You decide that you want to walk as little as possible; so you model this problem as a minimum spanning tree (MST) in order to find the path you'd have to take to walk as little as possible.

Suppose you use the variables $x_{i,j} = 1$ if edge $(i,j)$ is part of the tree and 0 otherwise.

\begin{enumerate}
\item (20 points) When modeling this problem as a MST you need to include a constraint that says you visit each roller coaster. Using the $x_{i,j}$ variables, write a concrete constraint that ensures at least one edge connected to roller coaster 3 is selected.

{\blu
\[
x_{1,3} + x_{2,3} + x_{3,4} + x_{3,5} + x_{3,6} + x_{3,7} \geq 1
\]
}


\item After implementing this model in python, your solver returns the following solution:

	\verb|The optimal solution is to select edges [1,2], [2,3], [3,5], [4,6], [4,7], [6,7]|
		\begin{enumerate}
		\item (15 points) What are the values of the $x_{i,j}$ variables corresponding to this solution?
{\blu
		\[
		x_{1,2}=x_{2,3}=x_{3,5}=x_{4,6} = x_{4,7} = x_{6,7} = 1
		\]
		
		All other variables equal to 0.
}
		\item (15 points) What is the total distanced traveled by this solution?
		{\blu
		\[
		10+10+23+3+9+3 = 58
		\]
		}
		\newpage
		\item (10 points) Is this solution optimal to your MST problem?
		{
		\blu
		No, there is a cycle on nodes 4, 6, and 7
		}
		\item (20 points) If this solution is optimal explain why. If the solution is not optimal, write which constraint(s) you would add to your model to exclude this solution.
		{\blu
		\[
		x_{4,6} + x_{4,7}+ x_{6,7} \leq 2
		\]
		}
		\end{enumerate}
\end{enumerate}

\begin{enumerate}[resume]
\item (10 points) Given a graph on $n$ nodes, how many edges do I need to choose to form a cycle?

{
\blu $n$ nodes form a cycle
}
\item (10 points) True or False, when solving a MST problem in python, we should implement \textbf{every} constraint in the model.

{\blu
False, there are an exponential number of subtour elimination constraints, we only implement them when we need them.
}

\end{enumerate}



\end{document}
